The Local Group in the Cosmic Web

### 2014-10-27 paper/referee_reply.tex

\documentclass{article}
\title{Reply to the first referee report on the draft {\it The Local Group in the Cosmic Web}}
\author{J.E. Forero-Romero \& R. Gonz\'alez}
\date{\today}
\begin{document}
\maketitle

We thank the referee for a thorough report on our draft. We have
addressed all the points stated in the report. The points raised by
the referee are boldfaced. Our reply follows each point.

@@

\section{Major Points}

\begin{itemize}

\item
{\bf One of the main aspects of the paper is the alignment between the
  three eigenvectors of the tidal tensor and the two vectors defined
  by Local Group analogues (the normal to their orbital plane and the
  line connecting the two). Figure 3 and Figure 4 show this (variants
  are shown in figure 5 \& 6 as well). What these figures lack is an
  estimation - a quantification - of the statistical significance of
  the result. This can be easily done by constructing 3xN "sister"
  samples with the same number of elements as the 2sigma, 3sigma and
  general samples, uniformly drawn in the interval [0,1] and comparing
  them. For example in the case of figure 3 \& 4 one could imagine
  plotting the 2 sigma spread in the cumulative distribution of such
  random distributions. In Fig 5 some kind of spread indicating the
  variance in the median computations could be included (along with
  the medians and spread for a uniform distribution). In Figure 6 the
  authors could also include an expectation from random
  distributions.}

We have followed the advice from the referee. Now Figures 3, 4, 5 and
6 include a shadowed region quantifying the expectation from a random
distribution. The captions include an explanation on how the numbers
were estimated.

Our estimation proceeds as follows. We construct a sample of 3D
vectors with the same number of elemets as the 2sigma sample. We use
the smaller sample to estimate the upper bound on the uncertainties.

These vectors have a random distribution. From them we build
the integrated $\mu$ distributions with respected to a fixed
vector. We repeat the exercise 10000 times to compute the median
together with the $5\%$ and $95\%$ percentiles for the quantities of
interest. In the case of Figures 3,4 and 6 it corresponds to the
fraction of elements with values $<\mu$; in the case of Figure 5 it
corresponds to the median value of $\mu$.

With these error bars we still find that the alignments are
significant different from the expectations of a random
distribution. We also find that the different alignments in the
different samples, at a fixed mass (Figure 6), are consistent between
themselves.

@@

\item
{\bf My other significant point is the smoothing scale. The study
  examines the web on a fixed scale namely ~1.4Mpc. However since the
  scale is fixed it measures different aspects of the environment for
  different LG analogues. This is explicitely shown in Fig2 left. A
  halo of mass 5e13Mdot could have a virial radius of upto 1 or
  1.3Mpc. For these haloes the smoothing is basically on the scale of
  Rvir. Whereas for haloes with masses of 5e11 Mdot the virial radius
  is probably less than 200kpc and your 1.4Mpc smoothing is equivalent
  to 7 times the virial radius.  Although I am quite sure that the
  tidal tensor eigenvectors are stable across these different scales,
  I'm not quite sure the web classification, web ellipticity or web
  prolateness are. Perhaps you should convince the reader of this
  issue.}

We tested the robustness of our results with a smoothing scale of 0.7
Mpc, from the $512^3$ grid data available on the Multidark
Database. This is now mentioned in the paper.

Concerning a larger smoothing scale we base the robustness on previously
published results. In Forero-Romero et al. 2009  we presented a
through study of the environment as defined by the Tweb in terms of
the two free parameters of the model: $\lambda_{th}$ and the smoothing
scale. In that work we changed the smothing scale from 0.5 Mpc/h up to
12.5 Mpc/h and quantified the changes in the volume and mass filling
fractions (VFF and MFF) for each web environment. We found that for
the values of $\lambda_{th}\approx 0.3$ the VFF and MFF only change on
the order of $5\%$. In a thorough paper by Cautun et al. 2014 they
also show that the web properties are insensitive to changes of factor
of $2$ on the smoothing scale.

@@

\item
{\bf I also want to note that the preferential accretion found by Libeskind et al 2014 shows a signal primarily along e3, but also defined as being away from e1. Indeed the accretion is somewhat planar in the e2-e3 plane. So I wouldn't say there is a contradiction.}

We have made explicit this point in the Discussion section.

\item
{\bf Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g. Aragon-Calvo et al 2007, Codis et al 2012, Trowland et al 2013, Libeskind et al 2013, among others), likely due to major mergers.}

We have included a paragraph on this in the Results section.

### 2014-10-27 paper/main.tex
main includes the bib file

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments; Yehuda Hoffman for insightful
conversations on the subject of the Local Group and the Cosmic Web;
and the referee Noam Libeskind  that helped us to clarify and
strenghten the results presented in the paper. 
\bibliographystyle{apj}
\bibliography{references}

>>>>

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments; Yehuda Hoffman for insightful
conversations on the subject of the Local Group and the Cosmic Web;
and the referee Noam Libeskind  that helped us to clarify and
strenghten the results presented in the paper. 
\bibliographystyle{apj}
%\bibliography{references} 
\begin{thebibliography}{48}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Alonso} {et~al.}(2014){Alonso}, {Eardley}, \&
  {Peacock}}]{Alonso2014}
{Alonso}, D., {Eardley}, E., \& {Peacock}, J.~A. 2014, ArXiv e-prints

\bibitem[{{Aragon-Calvo} {et~al.}(2011){Aragon-Calvo}, {Silk}, \&
  {Szalay}}]{2011MNRAS.415L..16A}
{Aragon-Calvo}, M.~A., {Silk}, J., \& {Szalay}, A.~S. 2011, \mnras, 415, L16

\bibitem[{{Arag{\'o}n-Calvo} {et~al.}(2007){Arag{\'o}n-Calvo}, {van de
  Weygaert}, {Jones}, \& {van der Hulst}}]{AragonCalvo2007}
{Arag{\'o}n-Calvo}, M.~A., {van de Weygaert}, R., {Jones}, B.~J.~T., \& {van
  der Hulst}, J.~M. 2007, \apjl, 655, L5

\bibitem[{{Bailin} {et~al.}(2008){Bailin}, {Power}, {Norberg}, {Zaritsky}, \&
  {Gibson}}]{2008MNRAS.390.1133B}
{Bailin}, J., {Power}, C., {Norberg}, P., {Zaritsky}, D., \& {Gibson}, B.~K.
  2008, \mnras, 390, 1133

\bibitem[{{Cautun} {et~al.}(2014){Cautun}, {van de Weygaert}, {Jones}, \&
  {Frenk}}]{Cautun2014}
{Cautun}, M., {van de Weygaert}, R., {Jones}, B.~J.~T., \& {Frenk}, C.~S. 2014,
  \mnras, 441, 2923

\bibitem[{{Codis} {et~al.}(2012){Codis}, {Pichon}, {Devriendt}, {Slyz},
  {Pogosyan}, {Dubois}, \& {Sousbie}}]{Codis2012}
{Codis}, S., {Pichon}, C., {Devriendt}, J., {Slyz}, A., {Pogosyan}, D.,
  {Dubois}, Y., \& {Sousbie}, T. 2012, \mnras, 427, 3320

\bibitem[{{Courtois} {et~al.}(2013){Courtois}, {Pomar{\`e}de}, {Tully},
  {Hoffman}, \& {Courtois}}]{2013AJ....146...69C}
{Courtois}, H.~M., {Pomar{\`e}de}, D., {Tully}, R.~B., {Hoffman}, Y., \&
  {Courtois}, D. 2013, \aj, 146, 69

\bibitem[{{Cox} \& {Loeb}(2008)}]{2008MNRAS.386..461C}
{Cox}, T.~J., \& {Loeb}, A. 2008, \mnras, 386, 461

\bibitem[{{Fakhouri} \& {Ma}(2009)}]{2009MNRAS.394.1825F}
{Fakhouri}, O., \& {Ma}, C.-P. 2009, \mnras, 394, 1825

\bibitem[{{Forero-Romero}(2009)}]{2009MNRAS.399..762F}
{Forero-Romero}, J.~E. 2009, \mnras, 399, 762

\bibitem[{{Forero-Romero} {et~al.}(2014){Forero-Romero}, {Contreras}, \&
  {Padilla}}]{ForeroRomero2014}
{Forero-Romero}, J.~E., {Contreras}, S., \& {Padilla}, N. 2014, \mnras, 443,
  1090

\bibitem[{{Forero-Romero} {et~al.}(2013){Forero-Romero}, {Hoffman},
  {Bustamante}, {Gottl{\"o}ber}, \& {Yepes}}]{2013ApJ...767L...5F}
{Forero-Romero}, J.~E., {Hoffman}, Y., {Bustamante}, S., {Gottl{\"o}ber}, S.,
  \& {Yepes}, G. 2013, \apjl, 767, L5

\bibitem[{{Forero-Romero} {et~al.}(2009){Forero-Romero}, {Hoffman},
  {Gottl{\"o}ber}, {Klypin}, \& {Yepes}}]{Tweb}
{Forero-Romero}, J.~E., {Hoffman}, Y., {Gottl{\"o}ber}, S., {Klypin}, A., \&
  {Yepes}, G. 2009, \mnras, 396, 1815

\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Hoffman}, {Yepes},
  {Gottl{\"o}ber}, {Piontek}, {Klypin}, \& {Steinmetz}}]{ForeroRomero2011}
{Forero-Romero}, J.~E., {Hoffman}, Y., {Yepes}, G., {Gottl{\"o}ber}, S.,
  {Piontek}, R., {Klypin}, A., \& {Steinmetz}, M. 2011, \mnras, 417, 1434

\bibitem[{{Gonz{\'a}lez} {et~al.}(2013){Gonz{\'a}lez}, {Kravtsov}, \&
  {Gnedin}}]{sat}
{Gonz{\'a}lez}, R.~E., {Kravtsov}, A.~V., \& {Gnedin}, N.~Y. 2013, \apj, 770,
  96

\bibitem[{{Gonz{\'a}lez} {et~al.}(2014){Gonz{\'a}lez}, {Kravtsov}, \&
  {Gnedin}}]{lganalogues}
---. 2014, \apj, 793, 91

\bibitem[{{Gonz{\'a}lez} \& {Padilla}(2010)}]{2010MNRAS.407.1449G}
{Gonz{\'a}lez}, R.~E., \& {Padilla}, N.~D. 2010, \mnras, 407, 1449

\bibitem[{{Hahn} {et~al.}(2007){Hahn}, {Carollo}, {Porciani}, \&
  {Dekel}}]{Hahn2007}
{Hahn}, O., {Carollo}, C.~M., {Porciani}, C., \& {Dekel}, A. 2007, \mnras, 381,
  41

\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
  \& {Wright}}]{hinshaw_etal13}
{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
  {Wright}, E.~L. 2013, \apjs, 208, 19

\bibitem[{{Karachentsev}(2005)}]{2005AJ....129..178K}
{Karachentsev}, I.~D. 2005, \aj, 129, 178

\bibitem[{{Klypin} {et~al.}(2003){Klypin}, {Hoffman}, {Kravtsov}, \&
  {Gottl{\"o}ber}}]{2003ApJ...596...19K}
{Klypin}, A., {Hoffman}, Y., {Kravtsov}, A.~V., \& {Gottl{\"o}ber}, S. 2003,
  \apj, 596, 19

\bibitem[{{Klypin} \& {Holtzman}(1997)}]{1997astro.ph.12217K}
{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints

\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
  {Primack}}]{2011ApJ...740..102K}
{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102

\bibitem[{{Kroupa} {et~al.}(2005){Kroupa}, {Theis}, \&
  {Boily}}]{2005A&A...431..517K}
{Kroupa}, P., {Theis}, C., \& {Boily}, C.~M. 2005, \aap, 431, 517

\bibitem[{{Lee} \& {Shandarin}(1998)}]{1998ApJ...500...14L}
{Lee}, J., \& {Shandarin}, S.~F. 1998, \apj, 500, 14

\bibitem[{{Lemson} \& {Kauffmann}(1999)}]{1999MNRAS.302..111L}
{Lemson}, G., \& {Kauffmann}, G. 1999, \mnras, 302, 111

\bibitem[{{Li} \& {White}(2008)}]{2008MNRAS.384.1459L}
{Li}, Y.-S., \& {White}, S.~D.~M. 2008, \mnras, 384, 1459

\bibitem[{{Libeskind} {et~al.}(2013){Libeskind}, {Hoffman}, {Forero-Romero},
  {Gottl{\"o}ber}, {Knebe}, {Steinmetz}, \& {Klypin}}]{Libeskind2013}
{Libeskind}, N.~I., {Hoffman}, Y., {Forero-Romero}, J., {Gottl{\"o}ber}, S.,
  {Knebe}, A., {Steinmetz}, M., \& {Klypin}, A. 2013, \mnras, 428, 2489

\bibitem[{{Libeskind} {et~al.}(2014){Libeskind}, {Knebe}, {Hoffman}, \&
  {Gottl{\"o}ber}}]{2014MNRAS.443.1274L}
{Libeskind}, N.~I., {Knebe}, A., {Hoffman}, Y., \& {Gottl{\"o}ber}, S. 2014,
  \mnras, 443, 1274

\bibitem[{{Mei} {et~al.}(2007){Mei}, {Blakeslee}, {C{\^o}t{\'e}}, {Tonry},
  {West}, {Ferrarese}, {Jord{\'a}n}, {Peng}, {Anthony}, \&
  {Merritt}}]{2007ApJ...655..144M}
{Mei}, S., {Blakeslee}, J.~P., {C{\^o}t{\'e}}, P., {Tonry}, J.~L., {West},
  M.~J., {Ferrarese}, L., {Jord{\'a}n}, A., {Peng}, E.~W., {Anthony}, A., \&
  {Merritt}, D. 2007, \apj, 655, 144

\bibitem[{{Mu{\~n}oz-Cuartas} {et~al.}(2011){Mu{\~n}oz-Cuartas}, {M{\"u}ller},
  \& {Forero-Romero}}]{2011MNRAS.417.1303M}
{Mu{\~n}oz-Cuartas}, J.~C., {M{\"u}ller}, V., \& {Forero-Romero}, J.~E. 2011,
  \mnras, 417, 1303

\bibitem[{{Nuza} {et~al.}(2014){Nuza}, {Kitaura}, {He{\ss}}, {Libeskind}, \&
  {M{\"u}ller}}]{2014MNRAS.445..988N}
{Nuza}, S.~E., {Kitaura}, F.-S., {He{\ss}}, S., {Libeskind}, N.~I., \&
  {M{\"u}ller}, V. 2014, \mnras, 445, 988

\bibitem[{{Pawlowski} {et~al.}(2014){Pawlowski}, {Famaey}, {Jerjen}, {Merritt},
  {Kroupa}, {Dabringhausen}, {L{\"u}ghausen}, {Forbes}, {Hensler}, {Hammer},
  {Puech}, {Fouquet}, {Flores}, \& {Yang}}]{Pawlowski2014}
{Pawlowski}, M.~S., {Famaey}, B., {Jerjen}, H., {Merritt}, D., {Kroupa}, P.,
  {Dabringhausen}, J., {L{\"u}ghausen}, F., {Forbes}, D.~A., {Hensler}, G.,
  {Hammer}, F., {Puech}, M., {Fouquet}, S., {Flores}, H., \& {Yang}, Y. 2014,
  \mnras, 442, 2362

\bibitem[{{Pawlowski} {et~al.}(2012){Pawlowski}, {Kroupa}, {Angus}, {de Boer},
  {Famaey}, \& {Hensler}}]{Pawlowski2012}
{Pawlowski}, M.~S., {Kroupa}, P., {Angus}, G., {de Boer}, K.~S., {Famaey}, B.,
  \& {Hensler}, G. 2012, \mnras, 424, 80

\bibitem[{{Pawlowski} {et~al.}(2013){Pawlowski}, {Kroupa}, \&
  {Jerjen}}]{Pawlowski2013}
{Pawlowski}, M.~S., {Kroupa}, P., \& {Jerjen}, H. 2013, \mnras, 435, 1928

\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
  {Turchaninov}}]{Riebe2013}
{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691

\bibitem[{{Sandage} \& {Tammann}(1975)}]{1975ApJ...196..313S}
{Sandage}, A., \& {Tammann}, G.~A. 1975, \apj, 196, 313

\bibitem[{{Shaya} \& {Tully}(2013)}]{Shaya2013}
{Shaya}, E.~J., \& {Tully}, R.~B. 2013, \mnras, 436, 2096

\bibitem[{{Sheth} \& {Tormen}(2004)}]{2004MNRAS.350.1385S}
{Sheth}, R.~K., \& {Tormen}, G. 2004, \mnras, 350, 1385

\bibitem[{{Sohn} {et~al.}(2012){Sohn}, {Anderson}, \& {van der
  Marel}}]{2012ApJ...753....7S}
{Sohn}, S.~T., {Anderson}, J., \& {van der Marel}, R.~P. 2012, \apj, 753, 7

\bibitem[{{Sousbie}(2011)}]{2011MNRAS.414..350S}
{Sousbie}, T. 2011, \mnras, 414, 350

\bibitem[{{Trowland} {et~al.}(2013){Trowland}, {Lewis}, \&
  {Bland-Hawthorn}}]{Trowland2013}
{Trowland}, H.~E., {Lewis}, G.~F., \& {Bland-Hawthorn}, J. 2013, \apj, 762, 72

\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{a}}){van der Marel}, {Besla},
  {Cox}, {Sohn}, \& {Anderson}}]{2012ApJ...753....9V}
{van der Marel}, R.~P., {Besla}, G., {Cox}, T.~J., {Sohn}, S.~T., \&
  {Anderson}, J. 2012{\natexlab{a}}, \apj, 753, 9

\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{b}}){van der Marel},
  {Fardal}, {Besla}, {Beaton}, {Sohn}, {Anderson}, {Brown}, \&
  {Guhathakurta}}]{2012ApJ...753....8V}
{van der Marel}, R.~P., {Fardal}, M., {Besla}, G., {Beaton}, R.~L., {Sohn},
  S.~T., {Anderson}, J., {Brown}, T., \& {Guhathakurta}, P. 2012{\natexlab{b}},
  \apj, 753, 8

\bibitem[{{Wang} {et~al.}(2009){Wang}, {Mo}, {Jing}, {Guo}, {van den Bosch}, \&
  {Yang}}]{2009MNRAS.394..398W}
{Wang}, H., {Mo}, H.~J., {Jing}, Y.~P., {Guo}, Y., {van den Bosch}, F.~C., \&
  {Yang}, X. 2009, \mnras, 394, 398

\bibitem[{{Wang} {et~al.}(2014){Wang}, {Mo}, {Yang}, {Jing}, \&
  {Lin}}]{2014ApJ...794...94W}
{Wang}, H., {Mo}, H.~J., {Yang}, X., {Jing}, Y.~P., \& {Lin}, W.~P. 2014, \apj,
  794, 94

\bibitem[{{Zentner} {et~al.}(2005){Zentner}, {Kravtsov}, {Gnedin}, \&
  {Klypin}}]{2005ApJ...629..219Z}
{Zentner}, A.~R., {Kravtsov}, A.~V., {Gnedin}, O.~Y., \& {Klypin}, A.~A. 2005,
  \apj, 629, 219

\bibitem[{{Zhang} {et~al.}(2009){Zhang}, {Yang}, {Faltenbacher}, {Springel},
  {Lin}, \& {Wang}}]{Zhang2009}
{Zhang}, Y., {Yang}, X., {Faltenbacher}, A., {Springel}, V., {Lin}, W., \&
  {Wang}, H. 2009, \apj, 706, 747

\end{thebibliography}
